Meta RL analyses

### 2019-02-19 meta_RL_analyses.Rmd
Analyzing lang meta

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_drop_03", "language_drop_05", "language_noncompositional")

@@

```{r}
language_d = load_d(results_dir, c("language", "language_drop_03", "language_drop_05", "language_noncompositional"), num_runs, "new_language_rewards")

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer"# "basic_only_one", "basic_only_one_ho",
                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               ), num_runs, "new_meta_true_losses")

@@

# embeddings

>>>>

result_subdirs = c("nometa",# "nometa_su_heldout", "nometa_random_holdout_longer", "nometa_only_one",  "nometa_only_one_ho",
                   "basic", #"basic_su_heldout", 
                   "basic_random_holdout_longer", # "basic_only_one", "basic_only_one_ho",
                   "language", "language_noncompositional", "language_simplified", "language_random_holdout", "language_meta")

@@

```{r}
language_d = load_d(results_dir, c("language", "language_simplified", "language_random_holdout", "language_meta", "language_noncompositional"), num_runs, "new_language_rewards")

@@

```{r}
meta_d = load_d(results_dir, c("basic", 
                               #"basic_su_heldout",
                               "basic_random_holdout_longer",# "basic_only_one", "basic_only_one_ho",
                               #"language", "language_drop_03", "language_drop_05", "language_noncompositional"
                               "language", "language_random_holdout", "language_simplified", "language_meta"
                               ), num_runs, "new_meta_true_losses")

@@

# language-induced meta mapping (true) evaluation

```{r}
lang_meta_d = load_d(results_dir, c("language_meta", "language_simplified"
                               ), num_runs, "new_language_meta_true_losses")

lang_meta_d = lang_meta_d %>%
  filter(epoch == 0) %>%
  mutate(is_su_ho=grepl("su_heldout", run_type),
         is_only_one=grepl("only_one$", run_type),
         is_only_one_ho=grepl("only_one_ho", run_type),
         is_random_ho=grepl("random", run_type),
         is_default=!(is_su_ho | is_random_ho | is_only_one)) %>%
  gather(map_str, reward, -c(run, run_type, named_run_type, epoch), -starts_with("is_")) %>%
  separate(map_str, c("meta_task", "source", "target"), sep="[\\.]+") %>%
  mutate(is_new = (is_default & (source %in% new_game_strs | target %in% new_game_strs)) | (is_random_ho & (source %in% new_game_strs_random_heldout | target %in% new_game_strs_random_heldout)) | (is_only_one & (source %in% new_game_strs_only_one | target %in% new_game_strs_only_one)) | (is_su_ho & (source %in% new_game_strs_su_heldout | target %in% new_game_strs_su_heldout))| (is_only_one_ho & (source %in% new_game_strs_only_one_ho | target %in% new_game_strs_only_one_ho)),
         is_new = factor(is_new, labels=c("Trained", "Held out")))
```

```{r}
avg_lang_meta_d = lang_meta_d %>%
  group_by(run_type, named_run_type, run, meta_task, is_new) %>%
  summarize(avg_reward = mean(reward)) %>%
  group_by(run_type, named_run_type, meta_task, is_new) %>%
  summarize(avg_avg_reward = mean(avg_reward), sd_avg_reward = sd(avg_reward),
            se_reward = sd_avg_reward/sqrt(n()), 
            ci_lo = avg_avg_reward - 1.96*se_reward, 
            ci_hi = avg_avg_reward + 1.96*se_reward)

```{r}
ggplot(avg_lang_meta_d, aes(x=meta_task, fill=is_new, y=avg_avg_reward)) +
  geom_bar(stat="identity", position="dodge") +
  geom_errorbar(aes(ymin=ci_lo, ymax=ci_hi), position="dodge") +
  scale_fill_brewer(palette="Set2") +
  facet_wrap(. ~ named_run_type)
```

```{r}
summary_plot(lang_meta_d %>%
               filter(epoch == 0),
             "meta_task", "reward", "is_new") +
  facet_wrap(. ~ named_run_type)  +
  guides(color=guide_legend(title=NULL)) +
  labs(x="Game type", y="Average reward") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# 
# ggsave("writing/figures/language_meta_mapping.png", width=5, height=3.5)
```
# embeddings
